---
title: "Vignette for recurpkg package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(recurpkg)
```
The package is designed for recursive sequence calculation. The formular for the recursive sequence is as following:

$X_n$ = $X_{n-1}$ + |$X_{n-2} - X_{n-3}$|/2

That is, element N is the sum of element N−1 and the absolute value of the difference between elements N−2 and N−3 divided by two where each element is a number. For example, if we let $x_1$=3, $x_2$=1, and $x_3$=10, then $x_4$ is

$x_4$ = 10 + |1 - 3|/2 = 11

Some examples about the package use

```{r}
recur_vec(x = c(2, 4, 3), n = 3)
```

```{r}
recur_vec(x = c(2, 4, 3), n = 4)
```

```{r}
recur_vec(x = c(2, 4, 3), n = 5)
```

For the recursive dataset calculation, the users are expected to submit a data frame with four columns:

  -The first three columns are the values of the three numeric to be input to the recursive sequence function defined above and the fourth column is the positive integer n for the sequence to be generated.
  
  -This function should return a line plot of the output values for the different values of n.
  
examlpe about the dataset function use

```{r}
my_data <- tibble::tribble(
  ~x, ~y, ~z, ~n,
  2,4,3,3,
  2,4,3,5,
  2,4,3,7,
  2,4,3,10,
  2,4,3,15,
  2,4,3,20,
  2,4,3,25
)

recur_dataset(my_data)
```

